% !TEX root = ../VPJ.tex
%
% configurations
%

% text field
%-> replace supervisor names with correct ones
\firstSupervisor{Prof. Dr.-Ing. Ulfert Meiners}
\secondSupervisor{Prof. Dr.-Ing. Jochen Maaß, Prof. Dr.-Ing. Michael Röther}

% text field
%-> replace title with your thesis title
\thesisTitle{Verbundprojekt 2018/2019}
\thesisTitleEN{Verbundprojekt 2018/2019}

%\thesisKind{VPJ}

% text field
%-> replace the key words with your own key words
\keywordsDE{Smart Kamera, Objekterkennung, Farbdetektion, Gehäusekonstruktion, PixyCam, Raspberry Pi}
\keywordsEN{Smart Camera, Objecttracking, Colordetection, Construction, PixyCam, Raspberry Pi}

% text field
%-> replace the text with a description of the thesis
\abstractDE{
Im Rahmen dieser Arbeit werden zwei Kamerasysteme verglichen, welche farbige Objekte auf einem Laufband erkennen und deren Farbe auswerten. Über verschiedene Schnittstellen wird die Auswertung ausgegeben. Dazu werden Anwendungen entworfen, welche die Auswertung auf einem der Systeme ermöglichen. Die Arbeit beschreibt außerdem die konkrete Implementierung des Quellcodes der entworfenen Anwendungen für eines der Kamerasysteme. Ein weiterer zentraler Punkt der Arbeit ist der Entwurf einer geeigneten Halterung für die Kamerasysteme.} 
\abstractEN{
In this thesis, two camera systems are compared, which recognize colored objects on a conveyor belt and evaluate their color. The evaluation is output via various interfaces. For this purpose, applications are designed, which enable the evaluation on one of the systems. The thesis also describes the implementation of the source code of the designed applications for one of the camera systems. Another point of the work is the design of a suitable holder for the camera systems.
} 

% text field
%-> replace jon with your name
\thesisAuthor{Daniel Friedrich}

% text field
%-> enter the submission date
\submissionDate{25. Mai 2019}

% switch - uncomment only one
%-> uncomment NDA or public
%\NDA{yes}
\NDA{no}

% switch - uncomment only one
%-> uncomment the study course you are in
%\studycourse{TI}
%\studycourse{AI}
%\studycourse{WI}
%\studycourse{BMT}
%\studycourse{MAI}
\studycourse{MAA}
